---
title: "Country Opportunities Report Template"
output:
  word_document:
    toc: yes
  html_document:
    toc: yes
    toc_float: yes
always_allow_html: yes    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Objectives of this report

- OHI+ Tanzania Team
- Stakeholder process
- Data Sharing
- Etc

# OHI Global Framework and Tanzania

Before discussing scores, data, or data gaps, we will go through each goal of the global assessment conceptually, to determine whether these goals each represent Tanzania.

Full descriptions of each goal at [ohi-science.org/ohi-global/goals](http://ohi-science.org/ohi-global/goals.html), and a presentation to walk through each goal described in this section is available [here](https://docs.google.com/presentation/d/1R5oIFpTAqVbVTe6LymA9_eyaihOb7o3oJ9O6J5TruiE/edit?usp=sharing)

```{r, child="goal-descriptions-recs.Rmd"}
# you can edit this "child" RMarkdown file directly, save, and it will be "knit" into this full report
```


# Global Data, Data Gaps, Opportunities


```{r, child="explore-global-data.Rmd"}
# you can edit this "child" RMarkdown file directly, save, and it will be "knit" into this full report
```


# Potential Assessment Regions

Global assessments assess the exclusive economic zone (EEZs) of coastal countries and territories ([see Global Supplemental Information](https://rawgit.com/OHI-Science/ohi-global/draft/global_supplement/Supplement.html#3_regions)). 

In Tanzania...

# Summary

